---
title: "Change detection task - Data description"
author: "Adriana F. Chavez"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: true
    highlight: tango
    fig_width: 10 
    fig_height: 5 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rmdformats)
```

# Task description:



# Data description

The data from this experiment is stored in the following `.RData` file:

```{r}
load("./archive/abrupt_gradual.Rdata")
```

This loads an object called `ag` which holds the data in four dimensions:

- First dimension (rows) indicate trial count
- Second dimension (columns) indicate the variables observed
- Third dimension (pages) indicates the condition
- Fourth dimension (repetition) indicates the participant.

```{r}
dim(ag)
```

```{r, echo=FALSE}
I <- dim(ag)[4]
J <- dim(ag)[3]
K <- dim(ag)[1]
colnames(ag) <- c("resp", "true", "mean", "velocity", "change", "rt")

p <- 15
c <- 1
```

There were `r I` participants in this experiment, which completed `r K` trials of each of the `r J` conditions included, with a total of `r ncol(data)` variables being recorded per trial. We'll describe these variables upon looking at the first 5 observations collected for participant `r p` in condition `r c`:

```{r, echo=FALSE}
ag[1:5,,c,p]
```

For each trial, we collect the following information:

1. Predicted location (`resp`) - 
2. The true location (`true`) - The location of the spaceship that the participant observes, measured in radians.
3. Mean location (`mean`) - The mean of the Normal
4. Velocity (`velocity`) - 
5. Change-points (`change`) - A binary variable indicating whether a change has occured or not
6. RTs (`rt`) - Response time in seconds



The four conditions 

## Conditions

```{r}
data_stationary <- ag[,,1,]
data_abrupt <- ag[,,2,]
data_gradual <- ag[,,3,]
data_mixed <- ag[,,4,]
```

### Stationary 


```{r}
unique(data_stationary[,"change",])
```

```{r}
unique(data_stationary[,"mean",])
```


### Abrupt

```{r}
abrupt_change <- data_abrupt[,"change",]
apply(abrupt_change, 2, table)
```

## Gradual

## Mixed